---
title: "<center>SubBioMon eDNA report<center>"
output:
  flexdashboard::flex_dashboard: 
    navbar:
      - { title: "Sardinia",align: left, href: "https://smartise.github.io/SubBioMon/Sardinia.html" }
      - { title: "Albania",align: left, href: "https://smartise.github.io/SubBioMon/Albania.html" }
      - { title: "Luxembourg",align: left, href: "https://smartise.github.io/SubBioMon/Luxembourg.html" }
      - { title: "Sampling",align: right, href: "https://smartise.github.io/SubBioMon/Sampling.html" }
      - {href: "mailto:olivier.collard@ulb.be", align: right, icon: fa-envelope }
      - {href: "https://www.linkedin.com/in/olivier-collard-71639720a/", align: right, icon: fa-linkedin }

    orientation: row
    theme: 
      version: 4
      bootswatch: minty
      
---
```{r, echo=FALSE, results='hide',message=FALSE}
library(plotly)
library(DT)
library(htmltools)
library(reactable)
library(bslib)
library(thematic)
```
## Row 1 {data-height="100," data-padding="15"}
### Welcome

Welcome to the <a href="https://www.sub-biomon.net">Sub-BioMon</a> eDNA report website. 

Here is presented all the eDNA data gathered during the Sub-BioMon project. The Sub-BioMon project aim to develop and test approaches to monitor subterranean biodiversity in karst. 

The Biodiversa+ funded project involve differnt partner across Europe: 

- Subterranean Biology Lab (SubBioLab) (University of Ljubljana, SLOVENIA)
- Evolutionary Biology & Ecology (EBE) lab (Université libre de Bruxelles BELGIUM)
- Dark World O (Università degli Studi dell'Aquila ITALY), the Eötvös Loránd University (HUNGARY) 
- National Museum of Natural History (LUXEMBURG), 
- Emil Racovita Institute of Speleology (Romanian Academy - Cluj-Napoca Branch ROMANIA)

## Row 2 {data-padding="15"}
### Sampling map

```{r}
load("MAP/map.Rdata")
map
```



